The Power of Unbiased Recursive Partitioning:\\ A Unifying View of CTree, MOB, and GUIDE

### 2020-02-14 pkg/partykit/inst/guideliketest/draft/draft.Rnw
corrected link to simulation code
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2982 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 5bd3dddf3ce29d54fcf8792ffed22efeb02440e0

\newpage
\section*{Computational details}
\label{sec:comp}
The applied implementation is based on the \proglang{R} package \pkg{partykit}
(version~\Sexpr{packageVersion("partykit")}) which is available 
on \proglang{R}-Forge at \url{https://R-Forge.R-project.org/projects/partykit/}.
The code to reproduce the simulation study is available in the supplement for this 
paper on arXiv.org E-Print Archive (\url{https://arxiv.org/}).

>>>>

\newpage
\section*{Computational details}
\label{sec:comp}
The applied implementation is based on the \proglang{R} package \pkg{partykit}
%(version~\Sexpr{packageVersion("partykit")}) 
(version~1.2.4) 
which is available on \proglang{R}-Forge at 
\url{https://R-Forge.R-project.org/projects/partykit/}.
The code to reproduce the simulation study is available at \url{https://eeecon.uibk.ac.at/~zeileis/news/power_partitioning/}.
